Preserving Reciprocal Consistency in \\ Distributed Graph Databases

### 2020-04-21 slides/s7-delta.tex
corrections++

\begin{frame}
  \frametitle{Protocol Design Considerations}
  Design Considerations:
  \begin{enumerate}
  \item Graph workloads exhibit high contention.
  \item Graph transactions tend to be long-lived than those in other databases.
  \end{enumerate}
\textbf{Protocol must permit multiple updates on the same record provided they are they are \textit{sufficiently} apart in time in ensure reciprocal consistency}
\end{frame}

\begin{frame}
  \frametitle{\tDelta Protocol}
  \begin{itemize}
  \item Fact: a transaction updating a distributed edge must update one edge pointer then \textbf{immediately} update the other.
  \item Rule: an update is permitted if the immediately preceding update was done at least $\Delta$ time before. Else, abort.
  \item Assumption: the time interval that elapses between completing at update at one end and starting at the other can be estimated, $\delta$. Choosing $\Delta > \delta$.
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{\tDelta Protocol}
  \begin{itemize}
  \item Reciprocal consistency is preserved if the time taken to complete am update at one end and start at other end remains less than  $\Delta$
  \item If $\Delta$ is exceeded then reciprocal inconsistency can occur
  \item Setting a large $\Delta$ tends to preserve consistency but leads to more aborted transactions
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Protocol Design Considerations}
     \uncover<1->{  Design considerations:}
  \begin{enumerate}
     \uncover<2->{  \item Graph workloads exhibit high contention}
     \uncover<3->{  \item Graph transactions tend to be longer-lived than those in other databases}
  \end{enumerate}
     \uncover<4->{\textbf{Protocol must permit multiple updates on the same distributed edge provided they are \textit{sufficiently} apart in time to ensure reciprocal consistency}}
\end{frame}

\begin{frame}
  \frametitle{\tDelta Protocol}
  \begin{itemize}
  \uncover<1->{  \item \textbf{Fact:} a transaction updating a distributed edge must update one edge pointer then \textbf{immediately} update the other}
  \uncover<2->{  \item \textbf{Rule:} an update is permitted if the immediately preceding update was done at least $\Delta$ time before. Else, abort}
  \uncover<3->{  \item \textbf{Assumption:} the time interval that elapses between completing an update at one edge pointer and starting at the other can be estimated to be $\delta$.}
    \uncover<4->{ \item \textbf{Parameter Selection:} Choose $\Delta > \delta$}
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{\tDelta Protocol}
  \begin{itemize}
    \uncover<1->{  \item Reciprocal consistency is preserved if the time taken to complete an update at one edge pointer and start at other remains less than $\Delta$}
    \uncover<2->{  \item If $\Delta$ is exceeded then reciprocal inconsistency and hence semantic corruption can occur}
      \uncover<3->{  \item Setting a large $\Delta$ tends to preserve consistency but leads to more aborted transactions}
  \end{itemize}
\end{frame}

### 2020-04-21 slides/s8-evaluation.tex
corrections++

\begin{frame}
  \frametitle{Performance Evaluation}
  Two metrics the following two metrics for various values of $\Delta$:
  \begin{itemize}
  \item Time taken for 10\% of a large database to be corrupt
    \item Number of transactions aborted per second
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Time until 10\% database corruption2 $\boldsymbol{log(U)}$ vs Transaction Arrival Rate $(\boldsymbol{\lambda})$}
  \begin{center}
    For $\Delta = 50ms$, time taken for 10\% database corruption is between to $1$-$75$ years
  \end{center}
    \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{./figures/delta}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Fraction of Aborts vs Transaction Arrival Rate $(\boldsymbol{\lambda})$}
  \begin{center}
    For $\Delta = 50 ms$, the fraction of aborts is between 1 − 5\%
  \end{center}
    \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{./figures/aborts}
  \end{figure}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Performance Evaluation}
 Through simulations the following two metrics for various values of $\Delta$ were evaluated:
  \begin{itemize}
  \item Time taken for 10\% of a large database to become semantically corrupt
    \item Fraction of transactions aborted per second
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Time until 10\% semantic corruption $\boldsymbol{log(U)}$ vs Transaction Arrival Rate $(\boldsymbol{\lambda})$}
  \begin{center}
    For $\Delta = 50ms$, time taken for 10\% of a large database to become semantically corrupt is between to $1$-$75$ years
  \end{center}
    \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{./figures/delta}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Fraction of Aborts $(\boldsymbol{\alpha})$ vs Transaction Arrival Rate $(\boldsymbol{\lambda})$}
  \begin{center}
    For $\Delta = 50 ms$, the fraction of aborts is between 1 − 5\%
  \end{center}
    \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{./figures/aborts}
  \end{figure}
\end{frame}
